Increasing User Engagement in a Volunteer-Based Ephemeral Evolutionary Computation System

### 2017-02-17 2017-EUROPAR/Gamification/paper.tex
Conclusion added
@JJ Please check if there is time,

>>>>

\section{Conclusions}
\label{sec:conclusions}

The objective of this work was to test the kind of impact 
applying a gamification technique has on user engagement in 
the {\sf NodIO} volunteer computing framework; In concordance with 
the results obtained in other 
browser-based volunteer systems, after 
applying the gamification techniques, user participation was increased.

One of the interesting future lines of work would be to look a bit
more closely at the behavior of users as they are participating  
in the web system.

Another line of work would be to study the possible negative effects of using  
gamification techniques to improve engagement, like cheating or
literally {\em gaming} the system to defeat competition. We already
found some hints of this behavior, but more subtle effect could be taking place. 
Finally, the refinement of the proposed framework will need
more case studies and further multi-disciplinary research.
